

```{r, echo=FALSE, results='asis'}
name = sub(".png","",strsplit(i, "group_")[[1]][2])
part = strsplit(name,"_")
cat("\n### Results from ",part[[1]][1]," vs ",part[[1]][2],"\n")
cat("\n")
cat("<img src=\"",paste("maplots",i,sep="/"),"\" alt=\"maplot plot\">","\n",sep="")
cat("\n")
cat("*MAplot for ", part[[1]][1]," vs ",part[[1]][2],":*")
```
Each dot is one gene. On the x-axis we have the mean normalized counts across all samples used in the analysis (that is both conditions). On the the y-axis we have the log fold change between the conditions. Triangles indicate that the gene in question has a higher/lower fold change than what fits on the plot. The red color means that the gene has a adjusted p-value less than `r I(pvalue)`. 


```{r, include=FALSE}
csv=paste(paste0("contrast_group_",name),".csv",sep="")
a = read.csv(paste0("./lists/",csv))
```

```{r, echo=FALSE}
a = read.csv(paste0("./lists/",csv))
a = a[1:10,1:6]
kable(head(a),caption="Top 10 DE genes" )
```

Table shows the top 10 DE genes, the ranking is based on the absolute log2 FC of the significant (at adjusted p-value of `r I(pvalue)`) genes. 
In the full DE list the normalized counts for each sample is also included (columns 7 to end).


```{r, echo=FALSE, results='asis'}
cat("**Download the full [DE gene list](./lists/",csv,")"," for ",part[[1]][1]," vs ",part[[1]][2], " here.**\n",sep="")
cat("\n")
```
