

```{r, echo=FALSE, results='asis'}
name = sub(".png","",strsplit(i, "group__")[[1]][2])
part = strsplit(name,"__")
cat("\n### Results from ",part[[1]][1]," vs ",part[[1]][2],"\n")
cat("\n")
cat("<img src=\"",paste("maplots",i,sep="/"),"\" alt=\"maplot plot\">","\n",sep="")
cat("\n")
cat("*MAplot for ", part[[1]][1]," vs ",part[[1]][2],":*")
```
Each dot is one gene. On the x-axis we have the mean normalized counts across all samples used in the analysis (that is both conditions). On the the y-axis we have the log fold change between the conditions. Triangles indicate that the gene in question has a higher/lower fold change than what fits on the plot. The red color means that the gene has an adjusted p-value less than `r I(pvalue)`. 

```{r,echo = FALSE, results='asis'}
j = sub("maplot","barplot",i)
cat("<img src=\"",paste("barplots",j,sep="/"),"\" alt=\"barplot plot\">","\n",sep="")
cat("\n")
cat("*Barplot of significant genes in ", part[[1]][1]," vs ",part[[1]][2],":*")
``` 
The proportions of significant (at adjusted p-value less then `r I(pvalue)`) up regulated genes (yellow colored) and down regulated (blue colored) genes using three different fold change thresholds: 0 (no threshold) , log2 > 1 (two times difference) and log2 > 2 (four times difference).    


```{r, include=FALSE}
csv=paste(paste0("contrast_group__",name),".csv",sep="")
a = read.table(paste0("./lists/",csv),sep=",",header=T)
```

```{r, echo=FALSE}
a = a[1:10,1:6]
kable(a,caption="Top 10 DE genes" )
```

Table shows the top 10 DE genes, the ranking is based on the absolute log2 FC of the significant (at adjusted p-value of `r I(pvalue)`) genes. 
In the full DE list the normalized counts for each sample is also included (columns 7 to end).


```{r, echo=FALSE, results='asis'}
cat("**Download the full [DE gene list](../deseq/",csv,")"," for ",part[[1]][1]," vs ",part[[1]][2], " here.**\n",sep="")
cat("\n")
```
